---
title: "ML Housing Price Data Prep"
author: "Will Thackway"
date: "02/07/2021"
output: html_document
---

############ 0. Setup ###################
# 0.0 Import packages
```{r setup}
library(sf)
library(dplyr)
library(MLmetrics)
library(mapview)

library(raster)
library(geomerge)
library(maptools)
library(tidyverse)
library(lwgeom)
library(plyr)
library(tmap)
library(ggplot2)
library(reshape2)
library(maptools)
library(rgdal)
library(zoo)

library(classInt)
library(Hmisc)
library(ExcelFunctionsR)
```

# 0.1 Assumption setting
```{r}
# Inflation Rate
inf_rate <- 0.025

# Property Count Threshold
pct <- 10
```



############ 1. Import & Clean Data ###################
# 1.1 Import Data, inflate property price 
```{r}
## Sold Data
nsw_property_07  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2007 - inc Geocode_57562_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2007, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^9) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_08  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2008 - inc Geocode_57561_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2008, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^8) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_09  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2009 - inc Geocode_57560_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2009, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^7) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_10  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2010 - inc Geocode_57559_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2010, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^6) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_11  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2011 - inc Geocode_57558_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2011, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2011, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^5) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_12  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2012 - inc Geocode_57557_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2012, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2012, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^4) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_13  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2013 - inc Geocode_57556_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2013, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2013, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^3) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_14  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2014 - inc Geocode_57555_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2014, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2014, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^2) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_15  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2015 - inc Geocode_57554_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2015, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2015, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^1) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_16  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2016 - inc Geocode_57552_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2016, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2016, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^0) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)


# Merge all datasets
nsw_property_05_16 <- rbind(#nsw_property_05, 
                            #nsw_property_06,
                            nsw_property_07,
                            nsw_property_08, 
                            nsw_property_09,
                            nsw_property_10,
                            nsw_property_11,
                            nsw_property_12,
                            nsw_property_13,
                            nsw_property_14,
                            nsw_property_15,
                            nsw_property_16) %>% drop_na()



## Rental Data
nsw_rent_07  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2007 - inc Geocode_57546_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2007, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^9) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_08  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2008 - inc Geocode_57537_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2008, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^8) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_09  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2009 - inc Geocode_57536_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2009, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^7) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_10  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2010 - inc Geocode_57905_20200715.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2010, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^6) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_11  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2011 - inc Geocode_57533_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2011, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^5) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_12  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2012 - inc Geocode_57530_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2012, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^4) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_13  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2013 - inc Geocode_57529_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2013, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^3) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_14  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2014 - inc Geocode_57528_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2014, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^2) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_15  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2015 - inc Geocode_57527_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2015, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^1) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_16  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2016 - inc Geocode_57526_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2016, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^0) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)


# Merge all datasets
nsw_rental_05_16 <- rbind(#nsw_rent_05, 
                          #nsw_rent_06, 
                          nsw_rent_07, 
                          nsw_rent_08, 
                          nsw_rent_09,
                          nsw_rent_10,
                          nsw_rent_11,
                          nsw_rent_12,
                          nsw_rent_13,
                          nsw_rent_14,
                          nsw_rent_15,
                          nsw_rent_16) %>% drop_na()
```



# 1.2 Merge dataset with SA1 => to get SA1 column
```{r}
# Import SA1 esri shapefile boundaries
# Import Statistical Area boundaries
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa1_2016_aust_shape.zip", exdir=".")
sa1 <- read_sf("SA1_2016_AUST.shp") %>% filter(GCC_CODE16 == "1GSYD") %>% st_transform(crs = st_crs(4283))

# Convert data to spatial data frame using property latitude and longitude
df_SF <- st_as_sf(nsw_property_05_16,coords = c("Property_Longitude", "Property_Latitude"), crs = st_crs(4283))

rdf_SF <- st_as_sf(nsw_rental_05_16,coords = c("Property_Longitude", "Property_Latitude"), crs = st_crs(4283))


# Merge points and polygon data
df_SF_sa1 <- sf::st_join(df_SF, sa1,  join = st_intersects) %>% drop_na()

rdf_SF_sa1 <- sf::st_join(rdf_SF, sa1,  join = st_intersects) %>% drop_na()
```



############ 2. Summarise Data ###################

# 2.1 Summarise median price inflated for two 5 year periods: SA1 Area
```{r}
# Drop geometry column in df to reduce computation time
df_sa1 <- df_SF_sa1
df_sa1$geometry <- NULL

rdf_sa1 <- rdf_SF_sa1
rdf_sa1$geometry <- NULL

# Separate out 5 year periods, separate into units and houses
house_11 <- df_sa1 %>% filter(year < 2012, year > 2006, PropertyCategorisation=="House")
house_16 <- df_sa1 %>% filter(year > 2011, PropertyCategorisation=="House")
unit_11 <- df_sa1 %>% filter(year < 2012, year > 2006, PropertyCategorisation=="Unit")
unit_16 <- df_sa1 %>% filter(year > 2011, PropertyCategorisation=="Unit")
rental_11 <- rdf_sa1 %>% filter(year < 2012, year > 2006)
rental_16 <- rdf_sa1 %>% filter(year > 2011)


# Summarise median price inflated for each SA1 area for each 5-year period, for units and houses
house_11_median_SA1 <- ddply(house_11, .(SA1_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
house_16_median_SA1 <- ddply(house_16, .(SA1_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf))

unit_11_median_SA1 <- ddply(unit_11, .(SA1_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
unit_16_median_SA1 <- ddply(unit_16, .(SA1_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf))

rental_11_median_SA1 <- ddply(rental_11, .(SA1_MAIN16), dplyr::summarize,
                              median_rental_inf = median(EventPriceInf),
                              count = length(EventPrice) )
rental_16_median_SA1 <- ddply(rental_16, .(SA1_MAIN16), dplyr::summarize,
                              median_rental_inf = median(EventPriceInf),
                              count = length(EventPrice) )
```


# 2.2 Summarise median price inflated for two 5 year periods: SA2 & SA3 Area
```{r}
## Property Prices
# Summarise median price inflated for each SA2 area for each 5-year period, for units and houses
house_11_median_SA2 <- ddply(house_11, .(SA2_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
house_16_median_SA2 <- ddply(house_16, .(SA2_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf))

unit_11_median_SA2 <- ddply(unit_11, .(SA2_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
unit_16_median_SA2 <- ddply(unit_16, .(SA2_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf))

# Summarise median price inflated for each SA3 area for each 5-year period, for units and houses
house_11_median_SA3 <- ddply(house_11, .(SA3_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
house_16_median_SA3 <- ddply(house_16, .(SA3_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )

unit_11_median_SA3 <- ddply(unit_11, .(SA3_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
unit_16_median_SA3 <- ddply(unit_16, .(SA3_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )



## Rental Prices
# SA2
rental_11_median_SA2 <- ddply(rental_11, .(SA2_MAIN16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
rental_16_median_SA2 <- ddply(rental_16, .(SA2_MAIN16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         count = length(EventPriceInf))

# SA3
rental_11_median_SA3 <- ddply(rental_11, .(SA3_CODE16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
rental_16_median_SA3 <- ddply(rental_16, .(SA3_CODE16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         count = length(EventPriceInf) )
```



########## 3. Impute missing SA1 property price values #########
# 3.1 Houses
```{r}
# SA1 11 -> 16 mapping
sa1_mapping <- read.csv("C:/Files/Value Australia/All_Projects/Data/Mappings/SA1 Mapping.csv", stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM")

# Import SA1 to SA2 mapping
sa1_csv <- read.csv("C:/Files/Value Australia/All_Projects/Data/Inputs/SA1_2016_AUST.csv", stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM") %>% 
  mutate(SA2_MAIN16 = SA2_MAINCODE_2016)

# Import population data => for anti-join with property price data
population_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Population.csv", stringsAsFactors = FALSE) %>% 
  mutate(SA1_MAIN16 = as.character(SA1_MAIN16))



## 2011
# Map 2011 data to SA2 Main code
house_11_median_mapped <- house_11_median_SA1 %>% 
  merge(sa1_csv, by="SA1_MAIN16") %>% 
  filter(count > pct) %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Find SA1 areas without mobility data, subsequently merge on SA1 -> SA2 mapping
house_11_median_nd <- anti_join(population_16, house_11_median_mapped, by="SA1_MAIN16") %>% 
  merge(sa1_csv, by="SA1_MAIN16")

# Merge on summarised SA2 data, to impute minimum SA2 values to SA1 areas with no property price data 
house_11_median_nd_wd <- merge(x=house_11_median_nd, y=house_11_median_SA2, by="SA2_MAIN16") %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Combine with original mobility dataset to obtain full 2011 mobility dataset
house_11_price <- rbind(house_11_median_mapped, house_11_median_nd_wd)

# Merge back on count data
house_11_comb <- merge(x=house_11_price, y=house_11_median_SA1[, c("SA1_MAIN16", "count")], by="SA1_MAIN16", all.x=TRUE)



## 2016
# Map 2016 data to SA2 Main code
house_16_median_mapped <- house_16_median_SA1 %>% 
  merge(sa1_csv, by="SA1_MAIN16") %>% 
  filter(count > pct) %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Find SA1 areas without mobility data, subsequently merge on SA1 -> SA2 mapping
house_16_median_nd <- anti_join(population_16, house_16_median_mapped, by="SA1_MAIN16") %>% 
  merge(sa1_csv, by="SA1_MAIN16")

# Merge on summarised SA2 data, to impute minimum SA2 values to SA1 areas with no property price data 
house_16_median_nd_wd <- merge(x=house_16_median_nd, y=house_16_median_SA2, by="SA2_MAIN16") %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Combine with original mobility dataset to obtain full 2011 mobility dataset
house_16_price <- rbind(house_16_median_mapped, house_16_median_nd_wd)

# Merge back on count data
house_16_comb <- merge(x=house_16_price, y=house_16_median_SA1[, c("SA1_MAIN16", "count")], by="SA1_MAIN16", all.x=TRUE)
```



# 3.2 Units
```{r}
## 2011
# Map 2011 data to SA2 Main code
unit_11_median_mapped <- unit_11_median_SA1 %>% 
  merge(sa1_csv, by="SA1_MAIN16") %>% 
  filter(count > pct) %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Find SA1 areas without mobility data, subsequently merge on SA1 -> SA2 mapping
unit_11_median_nd <- anti_join(population_16, unit_11_median_mapped, by="SA1_MAIN16") %>% 
  merge(sa1_csv, by="SA1_MAIN16")

# Merge on summarised SA2 data, to impute minimum SA2 values to SA1 areas with no property price data 
unit_11_median_nd_wd <- merge(x=unit_11_median_nd, y=unit_11_median_SA2, by="SA2_MAIN16") %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Combine with original mobility dataset to obtain full 2011 mobility dataset
unit_11_price <- rbind(unit_11_median_mapped, unit_11_median_nd_wd)

# Merge back on count data
unit_11_comb <- merge(x=unit_11_price, y=unit_11_median_SA1[, c("SA1_MAIN16", "count")], by="SA1_MAIN16", all.x=TRUE)




## 2016
# Map 2016 data to SA2 Main code
unit_16_median_mapped <- unit_16_median_SA1 %>% 
  merge(sa1_csv, by="SA1_MAIN16") %>% 
  filter(count > pct) %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Find SA1 areas without mobility data, subsequently merge on SA1 -> SA2 mapping
unit_16_median_nd <- anti_join(population_16, unit_16_median_mapped, by="SA1_MAIN16") %>% 
  merge(sa1_csv, by="SA1_MAIN16")

# Merge on summarised SA2 data, to impute minimum SA2 values to SA1 areas with no property price data 
unit_16_median_nd_wd <- merge(x=unit_16_median_nd, y=unit_16_median_SA2, by="SA2_MAIN16") %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_price_inf)

# Combine with original mobility dataset to obtain full 2011 mobility dataset
unit_16_price <- rbind(unit_16_median_mapped, unit_16_median_nd_wd)

# Merge back on count data
unit_16_comb <- merge(x=unit_16_price, y=unit_16_median_SA1[, c("SA1_MAIN16", "count")], by="SA1_MAIN16", all.x=TRUE)
```



# 3.3 Rental
```{r}
## 2011
# Map 2011 data to SA2 Main code
rental_11_median_mapped <- rental_11_median_SA1 %>% 
  merge(sa1_csv, by="SA1_MAIN16") %>% 
  filter(count > pct) %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_rental_inf)

# Find SA1 areas without mobility data, subsequently merge on SA1 -> SA2 mapping
rental_11_median_nd <- anti_join(population_16, rental_11_median_mapped, by="SA1_MAIN16") %>% 
  merge(sa1_csv, by="SA1_MAIN16")

# Merge on summarised SA2 data, to impute minimum SA2 values to SA1 areas with no property rental data 
rental_11_median_nd_wd <- merge(x=rental_11_median_nd, y=rental_11_median_SA2, by="SA2_MAIN16") %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_rental_inf)

# Combine with original mobility dataset to obtain full 2011 mobility dataset
rental_11_rental <- rbind(rental_11_median_mapped, rental_11_median_nd_wd)

# Merge back on count data
rental_11_comb <- merge(x=rental_11_rental, y=rental_11_median_SA1[, c("SA1_MAIN16", "count")], by="SA1_MAIN16", all.x=TRUE)


## 2016
# Map 2016 data to SA2 Main code
rental_16_median_mapped <- rental_16_median_SA1 %>% 
  merge(sa1_csv, by="SA1_MAIN16") %>% 
  filter(count > pct) %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_rental_inf)

# Find SA1 areas without mobility data, subsequently merge on SA1 -> SA2 mapping
rental_16_median_nd <- anti_join(population_16, rental_16_median_mapped, by="SA1_MAIN16") %>% 
  merge(sa1_csv, by="SA1_MAIN16")

# Merge on summarised SA2 data, to impute minimum SA2 values to SA1 areas with no property rental data 
rental_16_median_nd_wd <- merge(x=rental_16_median_nd, y=rental_16_median_SA2, by="SA2_MAIN16") %>% 
  dplyr::select(SA1_MAIN16, SA2_MAIN16, median_rental_inf)

# Combine with original mobility dataset to obtain full 2011 mobility dataset
rental_16_rental <- rbind(rental_16_median_mapped, rental_16_median_nd_wd)

# Merge back on count data
rental_16_comb <- merge(x=rental_16_rental, y=rental_16_median_SA1[, c("SA1_MAIN16", "count")], by="SA1_MAIN16", all.x=TRUE)
```



# 3.4 Combine Housing Price Dataset and Export
```{r}
# Merge Units and Houses Prices
property_11 <- merge(house_11_comb, unit_11_comb, by="SA1_MAIN16") %>% 
  merge(rental_11_comb, by="SA1_MAIN16") %>% 
  mutate(property_house_median_price = median_price_inf.x, 
         property_unit_median_price = median_price_inf.y,
         property_rental_median_price = median_rental_inf,
         property_house_number_sales = IFNA(count.x,0),
         property_unit_number_sales = IFNA(count.y,0),
         property_rental_number_bonds = IFNA(count, 0)) %>% 
  dplyr::select(SA1_MAIN16,
                property_house_median_price,
                property_house_number_sales,
                property_rental_median_price,
                property_unit_median_price,
                property_unit_number_sales,
                property_rental_number_bonds)

property_16 <- merge(house_16_comb, unit_16_comb, by="SA1_MAIN16") %>% 
  merge(rental_16_comb, by="SA1_MAIN16") %>% 
  mutate(property_house_median_price = median_price_inf.x, 
         property_unit_median_price = median_price_inf.y,
         property_rental_median_price = median_rental_inf,
         property_house_number_sales = IFNA(count.x,0),
         property_unit_number_sales = IFNA(count.y,0),
         property_rental_number_bonds = IFNA(count, 0)) %>% 
  dplyr::select(SA1_MAIN16,
                property_house_median_price,
                property_house_number_sales,
                property_rental_median_price,
                property_unit_median_price,
                property_unit_number_sales,
                property_rental_number_bonds)


# Export
write.csv(property_11, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Property.csv")
write.csv(property_16, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Property.csv")
```
