---
title: "Non-Census Data Cleaning"
author: "Will Thackway"
date: "07/07/2021"
output: html_document
---

############ 0. Setup ###################
# 0.0 Import packages
```{r setup}
library(sf)
library(dplyr)
library(MLmetrics)
library(mapview)

library(raster)
library(geomerge)
library(maptools)
library(tidyverse)
library(lwgeom)
library(plyr)
library(tmap)
library(ggplot2)
library(reshape2)
library(maptools)
library(rgdal)
library(zoo)

library(classInt)
library(Hmisc)
library(ExcelFunctionsR)
```


# 0. Import SA boundaries
```{r}
# SA1 Level
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa1_2016_aust_shape.zip", exdir=".")
sa1 <- st_read("SA1_2016_AUST.shp") %>% st_transform(crs = st_crs(4283)) %>% filter(STE_CODE16 == "1")

sa1_df <- sa1
sa1_df$geometry <- NULL
```


############ 1. Value Net Commercial Property Data ###################
# 1.1 Import Data
```{r}
# VG Dataset
vg_raw_sf <- readRDS("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/sf_SYD_Valnet_Dealing2001_2019.rds")

vg_raw_df <- readRDS("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/SYD_Valnet_dealing_Geocoded.rds")

# Population data to merge on data for SA1 areas without businesses
population_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Population.csv", stringsAsFactors = FALSE)
```

# 1.2 Investigate Descriptions
```{r}
# Summarise description field
vg_desc <- ddply(vg_raw_df, .(DESCRIPTION), summarise,  mean_price = length(PURCH_PRICE))

## Create commercial fields
# Define Descriptions for each field
industrial = c("INDUSTRIAL STRATA", "INDUST. STRATA - SALES OF PART INTERESTS", "INDUSTRIAL STRATA - SALE INCL. OTHER LANDS", "INDUST. VACANT. REAR LAND, BNDRY ADJ, ETC")

office = c("STRATA OFFICE", "OFFICES", "SHOPS/OFFICES", "STRATA OFFICE - SALE INCL. OTHER LANDS", "STRATA OFFICE - SALES OF PART INTERESTS", "OFFICES - SALES OF PART INTEREST", "OFFICES - SALE INCL. OTHER LANDS", "SHOPS & OFFICES - SALE OF PART INTERESTS", "SHOPS/OFFICES - SALE INCL. OTHER LANDS", "OFFICES / HERITAGE", "STRATA OFFICE / HERITAGE", "SHOPS/OFFICES / HERITAGE")

shops = c("SHOPS", "STRATA SHOP", "SHOPS - SALES OF PART INTERESTS", "SHOP AND DWELLING - CORNER STONE", "SHOPS - SALE INCL. OTHER LANDS", "STRATA SHOPS - SALES OF PART INTERESTS", "	STRATA SHOP - SALE INCL. OTHER LANDS", "SHOP & DWELLING - SALES OF PART OF INTERESTS", "REGIONAL SHOPPING CENTRE", "STRATA SHOPS - FLOOD PRONE", "SHOPS / HERITAGE", "SHOP/DWELLING (CNR STORE) - SALE INCL. OTHER LANDS", "REGIONAL SHOPPING CENTRE - SALE INCL. OTHER LANDS", "SHOPS/OFFICES / HERITAGE", "SHOPS & OFFICES - FLOOD PRONE")

factory_workshop_warehouse = c("FACTORY/WORKSHOP", "WAREHOUSE", "FACTORY/WORKSHOP - SALES OF PART INTERESTS", "FACTORY/W.SHOP - SALE INCL. OTHER LANDS", "WAREHOUSE - SALES OF PART INTERESTS", "WAREHOUSE - SALE INCL. OTHER LANDS", "FACTORY/WORKSHOP - FLOOD PRONE")

vg_comm <- vg_raw_df %>% 
  mutate(PropertyUse = ifelse(DESCRIPTION %in% industrial, "industrial",
                              ifelse(DESCRIPTION %in% office, "office",
                                     ifelse(DESCRIPTION %in% shops, "shops",
                                            ifelse(DESCRIPTION %in% factory_workshop_warehouse, "factory_warehouse_workshop",
                                                   "non-commercial") ) ) ) ,
         industrial = ifelse(PropertyUse == "industrial", 1, 0),
         office = ifelse(PropertyUse == "office", 1, 0),
         shops = ifelse(PropertyUse == "shops", 1, 0),
         factory_warehouse = ifelse(PropertyUse == "factory_warehouse_workshop", 1, 0),
         year = format(as.Date(CONT_DATE, format="%Y/%m/%d"),"%Y"))
```


# 1.3 Summarise number of commercial sales in 5-year periods before 2011 & 2016
```{r}
## Convert data to spatial data
# Import Statistical Area boundaries
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa1_2016_aust_shape.zip", exdir=".")
sa1 <- read_sf("SA1_2016_AUST.shp") %>% filter(GCC_CODE16 == "1GSYD") %>% st_transform(crs = st_crs(4283))

# Convert VG dataset to sf
vg_SF <- st_as_sf(vg_comm,coords = c("X_Centroid", "Y_Centroid"), crs = st_crs(4283))

# Merge datasets to get SA1 observation for 
vg_SF_sa1 <- sf::st_join(vg_SF, sa1,  join = st_intersects) %>% drop_na()


## Summarise based on 5 year periods
# Drop geometry column in df to reduce computation time
vg_df_sa1 <- vg_SF_sa1
vg_df_sa1$geometry <- NULL

# Separate into 5 year period before 2011 and 2016
vg_11 <- vg_df_sa1 %>% filter(year > 2006, year < 2012)
vg_16 <- vg_df_sa1 %>% filter(year > 2011, year < 2017)

# Merge with population data to fill in points for areas with no commercial sales
vg_11_all <- merge(x=population_16, y=vg_11, by="SA1_MAIN16", all.x=TRUE) %>% 
  mutate(industrial=IFNA(industrial, 0),
         office=IFNA(office, 0),
         shops=IFNA(shops, 0),
         factory_warehouse=IFNA(factory_warehouse, 0))

vg_16_all <- merge(x=population_16, y=vg_16, by="SA1_MAIN16", all.x=TRUE) %>% 
  mutate(industrial=IFNA(industrial, 0),
         office=IFNA(office, 0),
         shops=IFNA(shops, 0),
         factory_warehouse=IFNA(factory_warehouse, 0))

# Summarise number of commercial buildings sold in each SA1 area
vg_11_sum <- ddply(vg_11_all, .(SA1_MAIN16), summarise, 
                   commercial_industrial_sold = sum(industrial),
                   commercial_office_sold = sum(office),
                   commercial_shops_sold = sum(shops),
                   commercial_factory_warehouse_sold = sum(factory_warehouse))

vg_16_sum <- ddply(vg_16_all, .(SA1_MAIN16), summarise, 
                   commercial_industrial_sold = sum(industrial),
                   commercial_office_sold = sum(office),
                   commercial_shops_sold = sum(shops),
                   commercial_factory_warehouse_sold = sum(factory_warehouse))
```


# 1.4 Export Commercial Sold data
```{r}
write.csv(vg_11_sum, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Commercial.csv")

write.csv(vg_16_sum, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Commercial.csv")
```



########### 2. ABR Business Data ###################
# 2.1 Import Data
```{r}
# ABR data
abr_11_raw <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/2011_SA1_ABR.csv", stringsAsFactors = FALSE)

abr_16_raw <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/2016_SA1_ABR.csv", stringsAsFactors = FALSE)
```

# 2.2 Clean Data
```{r}
# Convert to wide format
abr_11_wide <- reshape(abr_11_raw, idvar = "SA1_MAIN16", timevar = "Industry_Class", direction = "wide")

abr_16_wide <- reshape(abr_16_raw, idvar = "SA1_MAIN16", timevar = "Industry_Class", direction = "wide")


# Merge ABN data with population dataset to generate points for SA1 areas without businesses
abr_11_all <- merge(x=population_16, y=abr_11_wide, by="SA1_MAIN16", all.x=TRUE)

abr_16_all <- merge(x=population_16, y=abr_16_wide, by="SA1_MAIN16", all.x=TRUE)

# Fill in NA's with 0
abr_11 <- abr_11_all %>% 
  mutate(cafe_rest = IFNA(Count.ABN.Cafes_and_Restaurants,0),
         pub_bar = IFNA(Count.ABN.Pubs_Taverns_and_Bars,0),
         clubs = IFNA(Count.ABN.Clubs_Hospitality,0),
         take_food = IFNA(Count.ABN.Takeaway_Food_Services,0),
         health_fitness = IFNA(Count.ABN.Health_and_Fitness_Centres_and_Gymnasia_Operation,0),
         sport_clubs = IFNA(Count.ABN.Sports_and_Physical_Recreation_Clubs_and_Sports_Professionals,0),
         sport_venues = IFNA(Count.ABN.Sports_and_Physical_Recreation_Venues_Grounds_and_Facilities_Operation,0)) %>% 
  dplyr::select(SA1_MAIN16,
                cafe_rest,
                pub_bar,
                clubs,
                take_food,
                health_fitness,
                sport_clubs,
                sport_venues)

abr_16 <- abr_16_all %>% 
  mutate(cafe_rest = IFNA(Count.ABN.Cafes_and_Restaurants,0),
         pub_bar = IFNA(Count.ABN.Pubs_Taverns_and_Bars,0),
         clubs = IFNA(Count.ABN.Clubs_Hospitality,0),
         take_food = IFNA(Count.ABN.Takeaway_Food_Services,0),
         health_fitness = IFNA(Count.ABN.Health_and_Fitness_Centres_and_Gymnasia_Operation,0),
         sport_clubs = IFNA(Count.ABN.Sports_and_Physical_Recreation_Clubs_and_Sports_Professionals,0),
         sport_venues = IFNA(Count.ABN.Sports_and_Physical_Recreation_Venues_Grounds_and_Facilities_Operation,0)) %>% 
  dplyr::select(SA1_MAIN16,
                cafe_rest,
                pub_bar,
                clubs,
                take_food,
                health_fitness,
                sport_clubs,
                sport_venues)
```


# 2.3 Export Data
```{r}
write.csv(abr_11, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_ABR.csv")

write.csv(abr_16, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_ABR.csv")
```



# 2.4 SA2-Level ABR
```{r}
# ABR data
abr_11_raw_SA2 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/2011_SA2_ABR.csv", stringsAsFactors = FALSE)

abr_16_raw_SA2 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/2016_SA2_ABR.csv", stringsAsFactors = FALSE)


# Convert to wide format
abr_11_wide_SA2 <- reshape(abr_11_raw_SA2, idvar = "SA2_NAME16", timevar = "Industry_Class", direction = "wide")

abr_16_wide_SA2 <- reshape(abr_16_raw_SA2, idvar = "SA2_NAME16", timevar = "Industry_Class", direction = "wide")


# Merge population data with SA1 dataset to get SA2 NAME for each SA1 area, to merge on ABR_SA2 data
population_16_sa1 <- merge(population_16, sa1_df, by="SA1_MAIN16")


# Merge ABN data with population dataset to generate points for SA1 areas without businesses
abr_11_all_sa2 <- merge(x=population_16_sa1, y=abr_11_wide_SA2, by="SA2_NAME16", all.x=TRUE)

abr_16_all_sa2 <- merge(x=population_16_sa1, y=abr_16_wide_SA2, by="SA2_NAME16", all.x=TRUE)


# Fill in NA's with 0
abr_11_sa2 <- abr_11_all_sa2 %>% 
  mutate(cafe_rest = IFNA(Count_ABN.Cafes_and_Restaurants,0),
         pub_bar = IFNA(Count_ABN.Pubs_Taverns_and_Bars,0),
         clubs = IFNA(Count_ABN.Clubs_Hospitality,0),
         take_food = IFNA(Count_ABN.Takeaway_Food_Services,0),
         health_fitness = IFNA(Count_ABN.Health_and_Fitness_Centres_and_Gymnasia_Operation,0),
         sport_clubs = IFNA(Count_ABN.Sports_and_Physical_Recreation_Clubs_and_Sports_Professionals,0),
         sport_venues = IFNA(Count_ABN.Sports_and_Physical_Recreation_Venues_Grounds_and_Facilities_Operation,0)) %>% 
  dplyr::select(SA1_MAIN16,
                cafe_rest,
                pub_bar,
                clubs,
                take_food,
                health_fitness,
                sport_clubs,
                sport_venues)

abr_16_sa2 <- abr_16_all_sa2 %>% 
  mutate(cafe_rest = IFNA(Count_ABN.Cafes_and_Restaurants,0),
         pub_bar = IFNA(Count_ABN.Pubs_Taverns_and_Bars,0),
         clubs = IFNA(Count_ABN.Clubs_Hospitality,0),
         take_food = IFNA(Count_ABN.Takeaway_Food_Services,0),
         health_fitness = IFNA(Count_ABN.Health_and_Fitness_Centres_and_Gymnasia_Operation,0),
         sport_clubs = IFNA(Count_ABN.Sports_and_Physical_Recreation_Clubs_and_Sports_Professionals,0),
         sport_venues = IFNA(Count_ABN.Sports_and_Physical_Recreation_Venues_Grounds_and_Facilities_Operation,0))  %>% 
  dplyr::select(SA1_MAIN16,
                cafe_rest,
                pub_bar,
                clubs,
                take_food,
                health_fitness,
                sport_clubs,
                sport_venues)


# Export Data
write.csv(abr_11_sa2, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA2_ABR.csv")

write.csv(abr_16_sa2, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA2_ABR.csv")
```



########### 3. Airbnb ###################
# 3.1 Import Data
```{r}
# Import Total Dwellings Data
dwellings_11 <- read.csv("C:/Files/Value Australia/Gentrification ML ML Prediction/Data/Inputs/2011 Census Data/2011_SA1_Dwellings_Total.csv")
dwellings_16 <- read.csv("C:/Files/Value Australia/Gentrification ML ML Prediction/Data/Inputs/2016 Census Data/2016_SA1_Dwellings_Total.csv")

# Import SA1 Mapping
sa1_mapping <- read.csv("C:/Files/Value Australia/All_Projects/Data/Mappings/SA1 Mapping.csv", stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM")

# Merge mapping onto dwellings 11 data
dwellings_11_mapped <- dwellings_11 %>% 
  merge(sa1_mapping, by="SA1_MAIN11")

# Merge on dwelling data to sa1 data
sa1_df <- sa1 
sa1_df$geometry <- NULL
sa1_df_1 <- merge(x=sa1_df, y=dwellings_11_mapped, by="SA1_MAIN16", all.x=TRUE)
sa1_df_2 <- merge(x=sa1_df_1, y=dwellings_16, by="SA1_MAIN16", all.x=TRUE) 

sa1_df_3 = sa1_df_2[!duplicated(sa1_df_2$SA1_MAIN16),]

# Import Airbnb data
airbnb_raw  <- read.csv("C:/Files/Value Australia/Airbnb Housing Prices/Data/Inputs/AirDNA_Extended_Australia_frontiersi_June_2021.csv", stringsAsFactors = FALSE) %>% 
  filter(City == "Sydney") %>% 
  mutate(Created.Date = as.Date(Created.Date), Last.Scraped.Date = as.Date(Last.Scraped.Date)) %>% 
  st_as_sf(coords = c("Longitude", "Latitude"), crs = st_crs(4283))
```


# 3.2 Create Airbnb Share measure
```{r}
# Merge on SA1 data
airbnb_sa1 <- st_join(airbnb_raw, sa1)

# Create active flags
airbnb <- airbnb_sa1 %>% 
  mutate(active_13 = ifelse(Created.Date < "2014-01-01" & Last.Scraped.Date > "2012-12-31", 1, 0),
         active_14 = ifelse(Created.Date < "2015-07-01" & Last.Scraped.Date > "2013-12-31", 1, 0),
         active_15 = ifelse(Created.Date < "2016-01-01" & Last.Scraped.Date > "2014-12-31", 1, 0),
         active_16 = ifelse(Created.Date < "2017-01-01" & Last.Scraped.Date > "2015-12-31", 1, 0)) 

# Separate active datasets
active_13 <- airbnb %>% filter(active_13 == 1)
active_14 <- airbnb %>% filter(active_14 == 1)
active_15 <- airbnb %>% filter(active_15 == 1)
active_16 <- airbnb %>% filter(active_16 == 1)
  

# Calculate number of listings in each SA1 level:
sa1_abb <- 
  sa1_df_3 %>%
  mutate(sa1_abb_count_13 = lengths(st_contains(sa1, active_13)),
         sa1_abb_count_14 = lengths(st_contains(sa1, active_14)),
         sa1_abb_count_15 = lengths(st_contains(sa1, active_15)),
         sa1_abb_count_16 = lengths(st_contains(sa1, active_16)),
         
         sa1_abb_share_13 = ifelse(Dwellings_Total_11 == 0, 0, IFNA(sa1_abb_count_13/Dwellings_Total_11,0)),
         sa1_abb_share_14 = ifelse(Dwellings_Total_11 == 0, 0, IFNA(sa1_abb_count_14/Dwellings_Total_11,0)),
         sa1_abb_share_15 = ifelse(Dwellings_Total_11 == 0, 0, IFNA(sa1_abb_count_15/Dwellings_Total_11,0)),
         sa1_abb_share_16 = ifelse(dwellings_total_16 == 0, 0, IFNA(sa1_abb_count_16/dwellings_total_16,0))
         ) %>%
  dplyr::select(SA1_MAIN16, sa1_abb_count_13, sa1_abb_count_14, sa1_abb_count_15, sa1_abb_count_16,
                sa1_abb_share_13, sa1_abb_share_14, sa1_abb_share_15, sa1_abb_share_16,
                Dwellings_Total_11, dwellings_total_16)

# Separate data into 2011 and 2016 datasets
sa1_abb_11 <- sa1_abb %>% 
  mutate(airbnb_count = sa1_abb_count_13,
         airbnb_share = sa1_abb_share_13) %>% 
  dplyr::select(SA1_MAIN16, airbnb_count, airbnb_share)

sa1_abb_16 <- sa1_abb %>% 
  mutate(airbnb_count = sa1_abb_count_16,
         airbnb_share = sa1_abb_share_16) %>% 
  dplyr::select(SA1_MAIN16, airbnb_count, airbnb_share)
```


# 3.3 Export Data
```{r}
write.csv(sa1_abb_11, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_ABB.csv")

write.csv(sa1_abb_16, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_ABB.csv")
```



########### 4. Mobility Measures ###################
# 4.1 Import Data
```{r}
## Import GCSA data to clip POI to within Greater Sydney
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_gccsa_2016_aust_shape.zip", exdir=".")
gcsa <- read_sf("GCCSA_2016_AUST.shp") %>% filter(GCC_CODE16 == "1GSYD") %>% st_transform(crs = st_crs(4283))

## TRANSPORT FACILITY POINT HISTORY
# The input file geodatabase
fgdb <- "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/Transport_facility_point.gdb"

# List all feature classes in a file geodatabase
subset(ogrDrivers(), grepl("GDB", name))
fc_list <- ogrListLayers(fgdb)
print(fc_list)

# Read the feature class
tfp <- readOGR(dsn=fgdb,layer="TransportFacilityPoint")
sf_tfp <- st_as_sf(tfp)
sf_tfp_syd <- st_transform(sf_tfp, crs = st_crs(4283)) %>% 
  st_join(gcsa) %>% 
  filter(GCC_CODE16 == "1GSYD")

# Convert to df
df_tfp <- sf_tfp_syd %>% cbind(st_coordinates(sf_tfp_syd))
df_tfp$geometry <- NULL



## POI HISTORICAL
# The input file geodatabase
fgdb2 <- "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/POIHistory_20210713.gdb"

# List all feature classes in a file geodatabase
subset(ogrDrivers(), grepl("GDB", name))
fc_list2 <- ogrListLayers(fgdb2)
print(fc_list2)

# Read the feature class
poi <- readOGR(dsn=fgdb2,layer="pointofinterest_history")
sf_poi <- st_as_sf(poi)
sf_poi_syd <- st_transform(sf_poi, crs = st_crs(4283)) %>% 
  st_join(gcsa) %>% 
  filter(GCC_CODE16 == "1GSYD")

# Convert to df
df_poi <- sf_poi_syd %>% cbind(st_coordinates(sf_poi_syd))
df_poi$geometry <- NULL


## Inspect POI Historical data
# Summarise types of POI
poi_sum <- ddply(df_poi, .(poitype), summarise,
                 count = length(poigroup))



## Save POI data
#write.csv(df_poi, "C:/Files/Value Australia/Gentrification Prediction/Data/Outputs/POIHistory_20210713_df.csv")
#saveRDS(sf_poi, "C:/Files/Value Australia/Gentrification Prediction/Data/Outputs/POIHistory_20210713_sf.rds")
```


# 4.2 Sub-Classifications and Broken down into active years
```{r}
## Transport Facility Point
# Write sub-class classifications
df_tfp <- df_tfp %>% mutate(point_type = ifelse(classsubtype ==1, "Airport", 
                                                ifelse(classsubtype ==2, "Bus Interchange",
                                                       ifelse(classsubtype ==4, "Marina",
                                                              ifelse(classsubtype ==5, "Carpark",
                                                                     ifelse(classsubtype ==6, "Railway/Light Rail",
                                                                            ifelse(classsubtype ==7, "Rest Area",
                                                                                   "Other")))))))

# Define new transport facility points within 5 year period before Census year
df_tfp_new_11 <- df_tfp %>% filter(startdate < "2012-01-01",
                               startdate > "2006-12-31")

df_tfp_new_16 <- df_tfp %>% filter(startdate < "2017-01-01",
                               startdate > "2011-12-31")
```



# 4.3 Export data 
```{r}
# Export TFP data
write.csv(df_tfp_new_11, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/TFP_New_11.csv")
write.csv(df_tfp_new_16, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/TFP_New_16.csv")
```