---
title: "ML Predictor Dataset Cleaning"
author: "Will Thackway"
date: "01/07/2021"
output: html_document
---

############ 0. Setup ###################
# 0.0 Packages
```{r setup, include=FALSE}
library(sf)
library(dplyr)
library(MLmetrics)
library(mapview)
library(ExcelFunctionsR)

library(raster)
library(geomerge)
library(maptools)
library(tidyverse)
library(lwgeom)
library(plyr)
library(tmap)
library(ggplot2)
library(reshape2)
library(maptools)
library(rgdal)
library(zoo)

library(classInt)
library(Hmisc)
```




############ 1. Import Data ###################
# 1.0 SEIFA scores
```{r}
SEIFA_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_SEIFA.csv", stringsAsFactors = FALSE)

SEIFA_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_SEIFA.csv", stringsAsFactors = FALSE)
```

# 1.1 Census Data
```{r}
## 2011 Datasets
age_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Age.csv", stringsAsFactors = FALSE)

cob_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_COB.csv", stringsAsFactors = FALSE)

dwelling_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Dwelling.csv", stringsAsFactors = FALSE)

education_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Education Level.csv", stringsAsFactors = FALSE)

employment_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Employment Status.csv", stringsAsFactors = FALSE)

family_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Family Composition.csv", stringsAsFactors = FALSE)

hours_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Hours Worked.csv", stringsAsFactors = FALSE)

income_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Income Weekly.csv", stringsAsFactors = FALSE)

industry_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Industry.csv", stringsAsFactors = FALSE)

marital_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Marital Status.csv", stringsAsFactors = FALSE)

migration_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Migration.csv", stringsAsFactors = FALSE)

occupation_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Occupation.csv", stringsAsFactors = FALSE)

population_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Population.csv", stringsAsFactors = FALSE)

religion_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Religion.csv", stringsAsFactors = FALSE)

tenure_06  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2006 Census Data/CSV Processed Inputs/2006_SA1_Tenure.csv", stringsAsFactors = FALSE)



## 2011 Datasets
age_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Age.csv", stringsAsFactors = FALSE)

cob_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_COB.csv", stringsAsFactors = FALSE)

dwelling_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Dwelling.csv", stringsAsFactors = FALSE)

education_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Education Level.csv", stringsAsFactors = FALSE)

employment_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Employment Status.csv", stringsAsFactors = FALSE)

family_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Family Composition.csv", stringsAsFactors = FALSE)

hours_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Hours Worked.csv", stringsAsFactors = FALSE)

income_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Median Income.csv", stringsAsFactors = FALSE)

industry_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Industry.csv", stringsAsFactors = FALSE)

marital_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Marital Status.csv", stringsAsFactors = FALSE)

migration_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Migration.csv", stringsAsFactors = FALSE)

occupation_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Occupation.csv", stringsAsFactors = FALSE)

population_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Population.csv", stringsAsFactors = FALSE) %>% mutate(SA1_MAIN11 = sa1_code)

religion_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Religion.csv", stringsAsFactors = FALSE)

tenure_11  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2011 Census Data/CSV Processed Inputs/2011_SA1_Tenure.csv", stringsAsFactors = FALSE)




## 2016 Datasets
age_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Age.csv", stringsAsFactors = FALSE)

cob_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_COB.csv", stringsAsFactors = FALSE)

dwelling_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Dwelling.csv", stringsAsFactors = FALSE)

education_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Education Level.csv", stringsAsFactors = FALSE)

employment_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Employment Status.csv", stringsAsFactors = FALSE)

family_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Family Composition.csv", stringsAsFactors = FALSE)

hours_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Hours Worked.csv", stringsAsFactors = FALSE)

income_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Median Income.csv", stringsAsFactors = FALSE)

industry_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Industry.csv", stringsAsFactors = FALSE)

marital_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Marital Status.csv", stringsAsFactors = FALSE)

migration_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Migration.csv", stringsAsFactors = FALSE)

occupation_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Occupation.csv", stringsAsFactors = FALSE)

population_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Population.csv", stringsAsFactors = FALSE)

religion_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Religion.csv", stringsAsFactors = FALSE)

tenure_16  <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/2016 Census Data/CSV Processed Inputs/2016_SA1_Tenure.csv", stringsAsFactors = FALSE)
```


# 1.2 Non-Census Data
```{r}
## 2006
#abb_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_ABB.csv")

abr_06 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2006_SA1_ABR.csv")

#commercial_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Commercial.csv")

#infra_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Infrastructure.csv")

property_06 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2006_SA1_Property.csv") %>%   mutate(property_house_number_sales = IFNA(property_house_number_sales, 0),
         property_unit_number_sales = IFNA(property_unit_number_sales, 0))

#walk_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Walkability.csv")



## 2011
abb_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_ABB.csv")

abr_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA2_ABR.csv")

commercial_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Commercial.csv")

infra_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Infrastructure.csv")

property_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Property.csv") %>% 
  mutate(property_house_number_sales = IFNA(property_house_number_sales, 0),
         property_unit_number_sales = IFNA(property_unit_number_sales, 0))

walk_11 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Walkability.csv")



## 2016
abb_16 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_ABB.csv")

abr_16 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA2_ABR.csv")

commercial_16 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Commercial.csv")

infra_16 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Infrastructure.csv")

property_16 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Property.csv") %>% 
  mutate(property_house_number_sales = IFNA(property_house_number_sales, 0),
         property_unit_number_sales = IFNA(property_unit_number_sales, 0))

walk_16 <- read.csv("C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Walkability.csv")
```


# 1.3 Import Mappings
```{r}
# SA1 11 -> 16 mapping
sa1_mapping <- read.csv("C:/Files/Value Australia/All_Projects/Data/Mappings/SA1 Mapping.csv", stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM")
```



######### 2. Merge Datasets ##########
# 2.1 Merge Predictor Variables
```{r}
# 2011, other than POW & Mobility data (which has already been mapped to 2016 SA1)
data_06 <- age_06 %>%
# Census Data
  merge(cob_06, by="SA1_MAIN11") %>% 
  merge(dwelling_06, by="SA1_MAIN11") %>% 
  merge(education_06, by="SA1_MAIN11") %>%
  merge(employment_06, by="SA1_MAIN11") %>%
  merge(family_06, by="SA1_MAIN11") %>%
#  merge(household_06, by="SA1_MAIN11") %>%
  merge(income_06, by="SA1_MAIN11") %>%
  merge(industry_06, by="SA1_MAIN11") %>%
  merge(marital_06, by="SA1_MAIN11") %>%
  merge(migration_06, by="SA1_MAIN11") %>%
  merge(occupation_06, by="SA1_MAIN11") %>%
  merge(population_06, by="SA1_MAIN11") %>%
  merge(religion_06, by="SA1_MAIN11") %>%
  merge(tenure_06, by="SA1_MAIN11") %>%
# SA1 mapping 
  merge(sa1_mapping, by="SA1_MAIN11") %>%           
# Non-Census data
#  merge(abb_06, by="SA1_MAIN16") %>% 
  merge(abr_06, by="SA1_MAIN16") %>% 
#  merge(commercial_06, by="SA1_MAIN16") %>% 
#  merge(infra_06, by="SA1_MAIN16") %>% 
  merge(property_06, by="SA1_MAIN16") %>% 
#  merge(walk_06, by="SA1_MAIN16") %>% 
# Drop NA's
  drop_na()

data_06_test <- data_06[!duplicated(data_06$SA1_MAIN16),]


# 2011
data_11 <- age_11 %>%
# Census Data
  merge(cob_11, by="SA1_MAIN11") %>% 
  merge(dwelling_11, by="SA1_MAIN11") %>% 
  merge(education_11, by="SA1_MAIN11") %>%
  merge(employment_11, by="SA1_MAIN11") %>%
  merge(family_11, by="SA1_MAIN11") %>%
#  merge(household_11, by="SA1_MAIN11") %>%
  merge(income_11, by="SA1_MAIN11") %>%
  merge(industry_11, by="SA1_MAIN11") %>%
  merge(marital_11, by="SA1_MAIN11") %>%
  merge(migration_11, by="SA1_MAIN11") %>%
  merge(occupation_11, by="SA1_MAIN11") %>%
  merge(population_11, by="SA1_MAIN11") %>%
  merge(religion_11, by="SA1_MAIN11") %>%
  merge(tenure_11, by="SA1_MAIN11") %>%
# SA1 mapping 
  merge(sa1_mapping, by="SA1_MAIN11") %>%           
# Non-Census data
  merge(abb_11, by="SA1_MAIN16") %>% 
  merge(abr_11, by="SA1_MAIN16") %>% 
  merge(commercial_11, by="SA1_MAIN16") %>% 
  merge(infra_11, by="SA1_MAIN16") %>% 
  merge(property_11, by="SA1_MAIN16") %>% 
  merge(walk_11, by="SA1_MAIN16") %>% 
# Drop NA's
  drop_na()

data_11_test <- data_11[!duplicated(data_11$SA1_MAIN16),]


# 2016
data_16 <- age_16 %>%
# Census Data
  merge(cob_16, by="SA1_MAIN16") %>% 
  merge(dwelling_16, by="SA1_MAIN16") %>% 
  merge(education_16, by="SA1_MAIN16") %>%
  merge(employment_16, by="SA1_MAIN16") %>%
  merge(family_16, by="SA1_MAIN16") %>%
#  merge(household_16, by="SA1_MAIN16") %>%
  merge(income_16, by="SA1_MAIN16") %>%
  merge(industry_16, by="SA1_MAIN16") %>%
  merge(marital_16, by="SA1_MAIN16") %>%
  merge(migration_16, by="SA1_MAIN16") %>%
  merge(occupation_16, by="SA1_MAIN16") %>%
  merge(population_16, by="SA1_MAIN16") %>%
  merge(religion_16, by="SA1_MAIN16") %>%
  merge(tenure_16, by="SA1_MAIN16") %>%
# Non-Census data
  merge(abb_16, by="SA1_MAIN16") %>% 
  merge(abr_16, by="SA1_MAIN16") %>% 
  merge(commercial_16, by="SA1_MAIN16") %>% 
  merge(infra_16, by="SA1_MAIN16") %>% 
  merge(property_16, by="SA1_MAIN16") %>% 
  merge(walk_16, by="SA1_MAIN16") %>% 
# Drop NA's
  drop_na()

data_16_test <- data_16[!duplicated(data_16$SA1_MAIN16),]


# write.csv(data_11_all, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Outputs/Data_11_All.csv")
```


# 2.2 Merge SEIFA data
```{r}
# 2006 - Finalise by dropping unnecessary variables
data_06_final <- data_06_test %>% 
  dplyr::select(-c(SA1_MAIN11, X.x, X.y))


# 2011 - Merge 2011 Predictor Variables to 2016 SEIFA score: ultimately we will use 2011 X to predict 2016 Y
data_11_SEIFA <- data_11 %>% 
  merge(SEIFA_11, by="SA1_MAIN11") %>% 
  merge(SEIFA_16, by="SA1_MAIN16") %>%
  mutate(irsad_score_11 = irsad_score.x,
         irsad_score_16 = irsad_score.y) %>% 
  dplyr::select(-c(sa1_code, SA1_MAIN11, airbnb_share, national_rank.x, national_rank.y, irsad_score.x, irsad_score.y, X.x, X, X.y))

data_11_SEIFA_final <- data_11_SEIFA[!duplicated(data_11_SEIFA$SA1_MAIN16),]

# 2016 - Don't merge on SEIFA score to 2016 dataset: ultimately we will use 2016 X to predict 2021 (unknown) Y
data_16_SEIFA <- data_16 %>% 
  merge(SEIFA_16, by="SA1_MAIN16") %>%
  dplyr::select(-c(area_sqkm, airbnb_share, national_rank, X.x, X.y, X))

data_16_SEIFA_final <- data_16_SEIFA[!duplicated(data_16_SEIFA$SA1_MAIN16),] 

# Test merging the two datasets to see how many SA1 areas compatible with both datasets
data_all_SEIFA <- merge(data_11_SEIFA_final, data_16_SEIFA_final, by="SA1_MAIN16") %>% drop_na()
```


# 2.3 Export Complete Dataset
```{r}
write.csv(data_06_final, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Cleaned Datasets/Data_06_final.csv")

write.csv(data_11_SEIFA_final, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Cleaned Datasets/Data_11_SEIFA_final.csv")

write.csv(data_16_SEIFA_final, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Cleaned Datasets/Data_16_SEIFA_final.csv")
```









######### 3. Visualisation
# 3.1 Import SA1 Boundaries
```{r}
# Import Statistical Area boundaries
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa1_2016_aust_shape.zip", exdir=".")
sa1 <- read_sf("SA1_2016_AUST.shp") %>% filter(GCC_CODE16 == "1GSYD")
```


# 3.2 sydney boundary
```{r}
# SA3 Outlines to narrow in on Sydney city
#unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa3_2016_aust_shape.zip", exdir=".")
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa3_2016_aust_shape.zip", exdir=".")
sa3 <- read_sf("SA3_2016_AUST.shp")

sa3_syd_sub <- c("Eastern Suburbs - North", "Eastern Suburbs - South",
                 "Botany", "Sydney Inner City", "Marrickville - Sydenham - Petersham",
                 "Leichhardt", "Kogarah - Rockdale", "Canterbury",
                 "Hurstville", "Strathfield - Burwood - Ashfield","Canada Bay",
                 "Bankstown", "Auburn", "Merrylands - Guildford", "Cronulla - Miranda - Caringbah",
                 "Sutherland - Menai - Heathcote", "Campbelltown (NSW)", "Liverpool", "Fairfield",
                 "Parramatta", "Blacktown", "Mount Druitt", "Blacktown - North",
                 "Baulkham Hills", "Carlingford", "Ryde - Hunters Hill", "North Sydney - Mosman",
                 "Chatswood - Lane Cove", "Manly", "Ku-ring-gai", "Warringah",
                 "Warringah", "Hornsby", "Dural - Wisemans Ferry", "Pittwater", "Rouse Hill - McGraths Hill",
                 "Campbelltown (NSW)", "Camden", "Bringelly - Green Valley", "Penrith",
                 "St Marys", "Richmond - Windsor", "Pennant Hills - Epping")

sa3_syd <- sa3 %>% 
  cbind(sa3, st_coordinates(st_centroid(sa3))) %>% 
  filter(SA3_NAME16 %in% sa3_syd_sub) 
```

# 3.3 Graph Population coverage for 2011 and 2016 datasets for knowledge of their catchment
```{r}
# Merge on sa1 boundaries to mobility dataset
data_all_sf <- merge(data_all_SEIFA, sa1_sf, by="SA1_MAIN16") %>% st_as_sf() %>% drop_na()

# Graph population coverage
population11 <- ggplot()+
  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="light grey") +
  geom_sf(data=data_all_sf, aes(x=X, y=Y, fill=population.x), colour="transparent") +
  scale_fill_viridis_c("Population 2011") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

population16 <- ggplot()+
  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="light grey") +
  geom_sf(data=data_all_sf, aes(x=X, y=Y, fill=population.y), colour="transparent") +
  scale_fill_viridis_c("Population 2016") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

population11
population11 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
population16
population16 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
```



# 3.4 Graph SEIFA coverage for 2011 and 2016 datasets for knowledge of their catchment
```{r}
# Graph population coverage
SEIFA11 <- ggplot()+
  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="light grey") +
  geom_sf(data=data_all_sf, aes(x=X, y=Y, fill=irsad_score.x), colour="transparent") +
  scale_fill_viridis_c("SEIFA Score 2011") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

SEIFA16 <- ggplot()+
  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="light grey") +
  geom_sf(data=data_all_sf, aes(x=X, y=Y, fill=irsad_score.y), colour="transparent") +
  scale_fill_viridis_c("SEIFA Score 2016") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

SEIFA11
SEIFA11 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
SEIFA16
SEIFA16 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
```









