---
title: "ML Housing Price Data Prep"
author: "Will Thackway"
date: "02/07/2021"
output: html_document
---

############ 0. Setup ###################
# 0.0 Import packages
```{r setup}
library(sf)
library(dplyr)
library(MLmetrics)
library(mapview)

library(raster)
library(geomerge)
library(maptools)
library(tidyverse)
library(lwgeom)
library(plyr)
library(tmap)
library(ggplot2)
library(reshape2)
library(maptools)
library(rgdal)
library(zoo)

library(classInt)
library(Hmisc)
library(ExcelFunctionsR)
```

# 0.1 Assumption setting
```{r}
# Inflation Rate
inf_rate <- 0.025

# Property Count Threshold
pct <- 10
```



############ 1. Import & Clean Data ###################
# 1.1 Import Data, inflate property price 
```{r}
## Sold Data
nsw_property_10  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2010 - inc Geocode_57559_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2012, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2010, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^11) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_11  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2011 - inc Geocode_57558_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2012, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2011, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^10) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_12  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2012 - inc Geocode_57557_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2012, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2012, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^9) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_13  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2013 - inc Geocode_57556_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2013, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2013, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^8) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_14  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2014 - inc Geocode_57555_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2014, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2014, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^7) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_15  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2015 - inc Geocode_57554_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2015, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2015, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^6) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_16  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2016 - inc Geocode_57552_20200624.csv", stringsAsFactors = FALSE) %>% mutate(year = 2016, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2016, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^5) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_17  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2017 - inc Geocode_57551_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2017, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^4) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_18  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2018 - inc Geocode_57550_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2018, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^3) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_19  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2019 - inc Geocode_57490_20200622.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2019, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^2) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_20  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 12 months to December 2020 - inc Geocode_62946_20210610.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2020, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^1) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)

nsw_property_21  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Sold/NSW Raw Sold data - 3 months to March 2021 - inc Geocode (3 months)_62948_20210610.csv", stringsAsFactors = FALSE) %>% mutate(year = 2011, EventDate = as.Date(EventDate, "%d/%m/%Y"), quarter = as.yearqtr(EventDate)) %>% 
  mutate(year = 2021, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^0) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, year, quarter, Postcode, Property_Latitude, Property_Longitude, PropertyCategorisation)


# Merge all datasets
nsw_property_10_21 <- rbind(nsw_property_10,
                            nsw_property_11,
                            nsw_property_12,
                            nsw_property_13,
                            nsw_property_14,
                            nsw_property_15,
                            nsw_property_16,
                            nsw_property_17,
                            nsw_property_18,
                            nsw_property_19,
                            nsw_property_20,
                            nsw_property_21) %>% drop_na()



## Rental Data
nsw_rent_10  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2010 - inc Geocode_57905_20200715.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2010, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^11) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_11  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2011 - inc Geocode_57533_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2011, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^10) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_12  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2012 - inc Geocode_57530_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2012, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^9) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_13  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2013 - inc Geocode_57529_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2013, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^8) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_14  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2014 - inc Geocode_57528_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2014, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^7) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_15  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2015 - inc Geocode_57527_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2015, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^6) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_16  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2016 - inc Geocode_57526_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2016, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^5) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_17  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2017 - inc Geocode_57525_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2017, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^4) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_18  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2018 - inc Geocode_57524_20200624.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2018, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^3) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_19  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2019 - inc Geocode_57492_20200623.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2019, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^2) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_20  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 12 months to December 2020 - inc Geocode_62940_20210610.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2020, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^1) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)

nsw_rent_21  <- read.csv("C:/Files/Value Australia/All_Projects/Ad Hoc/CL Macroeconomc Work/Property Data/Rental/NSW Raw data (FOR RENT) - 3 months to March 2021 - inc Geocode (3 months)_62941_20210610.csv", stringsAsFactors = FALSE) %>% 
  mutate(year = 2021, 
         EventDate = as.Date(EventDate, "%d/%m/%Y"), 
         quarter = as.yearqtr(EventDate),
         EventPriceInf = EventPrice * (1+inf_rate)^0) %>% 
  dplyr::select (EventDate, EventPrice, EventPriceInf, Suburb, Postcode, State, PropertyType, Property_Latitude, Property_Longitude, year, quarter)



# Merge all datasets
nsw_rental_10_21 <- rbind(nsw_rent_10,
                          nsw_rent_11,
                          nsw_rent_12,
                          nsw_rent_13,
                          nsw_rent_14,
                          nsw_rent_15,
                          nsw_rent_16,
                          nsw_rent_17,
                          nsw_rent_18,
                          nsw_rent_19,
                          nsw_rent_20,
                          nsw_rent_21) %>% drop_na()
```



# 1.2 Merge dataset with SA1 => to get SA1 column
```{r}
# Import SA1 esri shapefile boundaries
# Import Statistical Area boundaries
unzip("C:/Files/Value Australia/All_Projects/Data/Inputs/1270055001_sa1_2016_aust_shape.zip", exdir=".")
sa1 <- read_sf("SA1_2016_AUST.shp") %>% filter(GCC_CODE16 == "1GSYD") %>% st_transform(crs = st_crs(4283))

# Convert data to spatial data frame using property latitude and longitude
df_SF <- st_as_sf(nsw_property_10_21,coords = c("Property_Longitude", "Property_Latitude"), crs = st_crs(4283))

rdf_SF <- st_as_sf(nsw_rental_10_21,coords = c("Property_Longitude", "Property_Latitude"), crs = st_crs(4283))


# Merge points and polygon data
df_SF_sa1 <- sf::st_join(df_SF, sa1,  join = st_intersects) %>% drop_na()

rdf_SF_sa1 <- sf::st_join(rdf_SF, sa1,  join = st_intersects) %>% drop_na()
```



############ 2. Comparing 5-year period before each study period ###################

# 2.1 Summarise median price inflated for two 5 year periods: SA1 Area
```{r}
# Drop geometry column in df to reduce computation time
df_sa1 <- df_SF_sa1
df_sa1$geometry <- NULL

rdf_sa1 <- rdf_SF_sa1
rdf_sa1$geometry <- NULL

# Add column amalgamating gentrifying suburbs
df_sa1 <- df_sa1 %>% 
  mutate(SA2_NAME_gent = ifelse(SA2_NAME16 %in% c('Auburn - Central', 'Auburn - South', 'Auburn - North'), 'Auburn',
                                ifelse(SA2_NAME16 %in% c('Bankstown - South', 'Bankstown - North'), 'Bankstown',
                                       ifelse(SA2_NAME16 %in% c('Baulkham Hills (East)','Baulkham Hills (West) - Bella Vista',
                                                                'Eastwood - Denistone'), 'Eastwood - Baulkham Hills',
                                              ifelse(SA2_NAME16 %in% c('Maroubra - North','Maroubra - South','Maroubra - West'), 'Maroubra',
                                                     ifelse(SA2_NAME16 %in% c('Sutherland - Kirrawee', 'Oyster Bay - Como - Jannali'),
                                                            'Sutherland',
                                                            ifelse(SA2_NAME16 %in% c('Freshwater - Brookvale', 'Manly Vale - Allambie Heights'),
                                                                   'Brookvale', 
                                                                   SA2_NAME16 ) )  ) ) ) ) )

rdf_sa1 <- rdf_sa1 %>% 
  mutate(SA2_NAME_gent = ifelse(SA2_NAME16 %in% c('Auburn - Central', 'Auburn - South', 'Auburn - North'), 'Auburn',
                                ifelse(SA2_NAME16 %in% c('Bankstown - South', 'Bankstown - North'), 'Bankstown',
                                       ifelse(SA2_NAME16 %in% c('Baulkham Hills (East)','Baulkham Hills (West) - Bella Vista',
                                                                'Eastwood - Denistone'), 'Eastwood - Baulkham Hills',
                                              ifelse(SA2_NAME16 %in% c('Maroubra - North','Maroubra - South', 'Maroubra - West'), 'Maroubra',
                                                     ifelse(SA2_NAME16 %in% c('Sutherland - Kirrawee', 'Oyster Bay - Como - Jannali'),
                                                            'Sutherland',
                                                            ifelse(SA2_NAME16 %in% c('Freshwater - Brookvale', 'Manly Vale - Allambie Heights'),
                                                                   'Brookvale', 
                                                                   SA2_NAME16 ) )  ) ) ) ) )

# Separate out 5 year periods, separate into units and houses
house_16 <- df_sa1 %>% filter(year < 2017, year > 2011, PropertyCategorisation=="House")
house_21 <- df_sa1 %>% filter(year > 2016, PropertyCategorisation=="House")
unit_16 <- df_sa1 %>% filter(year < 2017, year > 2011, PropertyCategorisation=="Unit")
unit_21 <- df_sa1 %>% filter(year > 2016, PropertyCategorisation=="Unit")
property_16 <- df_sa1 %>% filter(year < 2017, year > 2006)
property_21 <- df_sa1 %>% filter(year > 2016)

rental_16 <- rdf_sa1 %>% filter(year < 2017, year > 2006)
rental_21 <- rdf_sa1 %>% filter(year > 2016)
```


# 2.2 Summarise median price inflated for two 5 year periods: SA2 & SA3 Area
```{r}
## Property Prices
# Summarise median price inflated for each SA2 area for each 5-year period, for units and houses
property_16_median_SA2 <- ddply(property_16, .(SA2_MAIN16, SA2_NAME16, GCC_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         count = length(EventPriceInf) )
property_21_median_SA2 <- ddply(property_21, .(SA2_MAIN16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         count = length(EventPriceInf))


house_16_median_SA2 <- ddply(house_16, .(SA2_MAIN16), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         count = length(EventPriceInf) )
house_21_median_SA2 <- ddply(house_21, .(SA2_MAIN16), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         count = length(EventPriceInf))


unit_16_median_SA2 <- ddply(unit_16, .(SA2_MAIN16), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         count = length(EventPriceInf) )
unit_21_median_SA2 <- ddply(unit_21, .(SA2_MAIN16), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         count = length(EventPriceInf))


# Summarise median price inflated for each SA3 area for each 5-year period, for units and houses
property_16_median_SA3 <- ddply(property_16, .(SA3_NAME16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         count = length(EventPriceInf) )
property_21_median_SA3 <- ddply(property_21, .(SA3_NAME16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         count = length(EventPriceInf))



## Rental Prices
# SA2
rental_16_median_SA2 <- ddply(rental_16, .(SA2_MAIN16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         count = length(EventPriceInf) )
rental_21_median_SA2 <- ddply(rental_21, .(SA2_MAIN16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         count = length(EventPriceInf))

# SA3
rental_16_median_SA3 <- ddply(rental_16, .(SA3_CODE16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         count = length(EventPriceInf) )
rental_21_median_SA3 <- ddply(rental_21, .(SA3_CODE16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         count = length(EventPriceInf) )
```



# 2.3 Combine Housing Price Dataset and Export
```{r}
# Merge Units and Houses Prices
overall_property <- property_16_median_SA2 %>% 
  merge(property_21_median_SA2, by="SA2_MAIN16") %>% 
  merge(house_16_median_SA2, by="SA2_MAIN16") %>% 
  merge(house_21_median_SA2, by="SA2_MAIN16") %>% 
  merge(unit_16_median_SA2, by="SA2_MAIN16") %>% 
  merge(unit_21_median_SA2, by="SA2_MAIN16") %>% 
  merge(rental_16_median_SA2, by="SA2_MAIN16") %>% 
  merge(rental_21_median_SA2, by="SA2_MAIN16") %>% 
  mutate(property_price_16 = median_price.x,
         property_price_21 = median_price.y,
         house_price_16 = house_price.x,
         house_price_21 = house_price.y,
         unit_price_16 = unit_price.x,
         unit_price_21 = unit_price.y,
         rental_price_16 = median_rental.x,
         rental_price_21 = median_rental.y,
         property_price_change = median_price.y - median_price.x,
         property_price_perc = (median_price.y - median_price.x)/median_price.x,
         house_price_change = house_price.y - house_price.x,
         house_price_perc = (house_price.y - house_price.x)/house_price.x,
         unit_price_change = unit_price.y - unit_price.x,
         unit_price_perc = (unit_price.y - unit_price.x)/unit_price.x,
         rental_price_change = median_rental.y - median_rental.x,
         rental_price_perc = (median_rental.y - median_rental.x)/median_rental.x) %>% 
  dplyr::select(SA2_MAIN16,
                SA2_NAME16,
                GCC_CODE16,
                property_price_16,
                property_price_21,
                house_price_16,
                house_price_21,
                unit_price_16,
                unit_price_21,
                rental_price_16,
                rental_price_21,
                property_price_change,
                property_price_perc,
                house_price_change,
                house_price_perc,
                unit_price_change,
                unit_price_perc,
                rental_price_change,
                rental_price_perc)

# Separate out to Sydney
overall_gsyd <- overall_property %>% 
  filter(GCC_CODE16 == "1GSYD")

median_house_perc_syd <- median(overall_gsyd$house_price_perc)



# Export
write.csv(property_06, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2006_SA1_Property.csv")
write.csv(property_11, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2011_SA1_Property.csv")
write.csv(property_16, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Inputs/Non-Census Data/CSV_Processed_Inputs/2016_SA1_Property.csv")
```



########## 3. Compare distinct years #############
# 3.1 Compare 10-years apart - gentrification areas amalgamated
```{r}
# Create datasets
house_2010 <- df_sa1 %>% filter(year == 2010, PropertyCategorisation=="House")
house_2020 <- df_sa1 %>% filter(year == 2020, PropertyCategorisation=="House")
unit_2010 <- df_sa1 %>% filter(year == 2010, PropertyCategorisation=="Unit")
unit_2020 <- df_sa1 %>% filter(year == 2020, PropertyCategorisation=="Unit")
property_2010 <- df_sa1 %>% filter(year == 2010)
property_2020 <- df_sa1 %>% filter(year == 2020)

rental_2010 <- rdf_sa1 %>% filter(year == 2010)
rental_2020 <- rdf_sa1 %>% filter(year == 2020)


# Summarise price for each year
property_2010_median_SA2 <- ddply(property_2010, .(SA2_NAME_gent, GCC_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         property_count = length(EventPriceInf) )
property_2020_median_SA2 <- ddply(property_2020, .(SA2_NAME_gent), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         property_count = length(EventPriceInf))


house_2010_median_SA2 <- ddply(house_2010, .(SA2_NAME_gent), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         house_count = length(EventPriceInf) )
house_2020_median_SA2 <- ddply(house_2020, .(SA2_NAME_gent), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         house_count = length(EventPriceInf))


unit_2010_median_SA2 <- ddply(unit_2010, .(SA2_NAME_gent), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         unit_count = length(EventPriceInf) )
unit_2020_median_SA2 <- ddply(unit_2020, .(SA2_NAME_gent), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         unit_count = length(EventPriceInf))


rental_2010_median_SA2 <- ddply(rental_2010, .(SA2_NAME_gent), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         rental_count = length(EventPriceInf) )
rental_2020_median_SA2 <- ddply(rental_2020, .(SA2_NAME_gent), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         rental_count = length(EventPriceInf))



# Merge into one dataset
overall_property_1020 <- property_2010_median_SA2 %>% 
  merge(property_2020_median_SA2, by="SA2_NAME_gent") %>% 
  merge(house_2010_median_SA2, by="SA2_NAME_gent") %>% 
  merge(house_2020_median_SA2, by="SA2_NAME_gent") %>% 
  merge(unit_2010_median_SA2, by="SA2_NAME_gent") %>% 
  merge(unit_2020_median_SA2, by="SA2_NAME_gent") %>% 
  merge(rental_2010_median_SA2, by="SA2_NAME_gent") %>% 
  merge(rental_2020_median_SA2, by="SA2_NAME_gent") %>% 
  mutate(property_price_2010 = median_price.x,
         property_price_2020 = median_price.y,
         house_price_2010 = house_price.x,
         house_price_2020 = house_price.y,
         unit_price_2010 = unit_price.x,
         unit_price_2020 = unit_price.y,
         rental_price_2010 = median_rental.x,
         rental_price_2020 = median_rental.y,
         property_count_2010 = property_count.x,
         property_count_2020 = property_count.y,
         house_count_2010 = house_count.x,
         house_count_2020 = house_count.y,
         unit_count_2010 = unit_count.x,
         unit_count_2020 = unit_count.y,
         rental_count_2010 = rental_count.x,
         rental_count_2020 = rental_count.y,
         property_price_change = median_price.y - median_price.x,
         property_price_perc = (median_price.y - median_price.x)/median_price.x,
         house_price_change = house_price.y - house_price.x,
         house_price_perc = (house_price.y - house_price.x)/house_price.x,
         unit_price_change = unit_price.y - unit_price.x,
         unit_price_perc = (unit_price.y - unit_price.x)/unit_price.x,
         rental_price_change = median_rental.y - median_rental.x,
         rental_price_perc = (median_rental.y - median_rental.x)/median_rental.x) %>% 
  dplyr::select(SA2_NAME_gent,
                GCC_CODE16,
                property_price_2010,
                property_price_2020,
                house_price_2010,
                house_price_2020,
                unit_price_2010,
                unit_price_2020,
                rental_price_2010,
                rental_price_2020,
                property_count_2010,
                property_count_2020,
                house_count_2010,
                house_count_2020,
                unit_count_2010,
                unit_count_2020,
                rental_count_2010,
                rental_count_2020,
                property_price_change,
                property_price_perc,
                house_price_change,
                house_price_perc,
                unit_price_change,
                unit_price_perc,
                rental_price_change,
                rental_price_perc)


# Gentrification [predicted] hotspots
hotspots <- c('Auburn - Central',
              'Auburn - South',
              'Auburn - North',
              'Bankstown - South',
              'Bankstown - North',
              'Baulkham Hills (East)',
              'Baulkham Hills (West) - Bella Vista',
              'Botany',
              'Eastwood - Denistone',
              'Maroubra - North',
              'Maroubra - South',
              'Maroubra - West',
              'Sutherland - Kirrawee')

hotspots2 <- c('Auburn',
              'Bankstown',
              'Eastwood - Baulkham Hills',
              'Botany',
              'Brookvale',
              'Maroubra',
              'Sutherland')

#gent_property_1020 <- overall_property_1020 %>% 
#  filter(SA2_NAME16 %in% hotspots)

gent_property_1020 <- overall_property_1020 %>% 
  filter(SA2_NAME_gent %in% hotspots2)


## Export datasets
write.csv(overall_property_1020, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Outputs/Property Validation/overall_property_1020_sa2.csv")
write.csv(gent_property_1020, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Outputs/Property Validation/gent_property_1020_sa2.csv")
```



# 3.2 Get Sydney-wide medians
```{r}
# Summarise price for each year
property_2010_median_GCC <- ddply(property_2010, .(GCC_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         property_count = length(EventPriceInf) )
property_2020_median_GCC <- ddply(property_2020, .(GCC_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         property_count = length(EventPriceInf))


house_2010_median_GCC <- ddply(house_2010, .(GCC_CODE16), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         house_count = length(EventPriceInf) )
house_2020_median_GCC <- ddply(house_2020, .(GCC_CODE16), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         house_count = length(EventPriceInf))


unit_2010_median_GCC <- ddply(unit_2010, .(GCC_CODE16), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         unit_count = length(EventPriceInf) )
unit_2020_median_GCC <- ddply(unit_2020, .(GCC_CODE16), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         unit_count = length(EventPriceInf))


rental_2010_median_GCC <- ddply(rental_2010, .(GCC_CODE16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         rental_count = length(EventPriceInf) )
rental_2020_median_GCC <- ddply(rental_2020, .(GCC_CODE16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         rental_count = length(EventPriceInf))


# Combine to one dataset
gcc_property_1020 <- property_2010_median_GCC %>% 
  merge(property_2020_median_GCC, by="GCC_CODE16") %>% 
  merge(house_2010_median_GCC, by="GCC_CODE16") %>% 
  merge(house_2020_median_GCC, by="GCC_CODE16") %>% 
  merge(unit_2010_median_GCC, by="GCC_CODE16") %>% 
  merge(unit_2020_median_GCC, by="GCC_CODE16") %>% 
  merge(rental_2010_median_GCC, by="GCC_CODE16") %>% 
  merge(rental_2020_median_GCC, by="GCC_CODE16") %>% 
  mutate(property_price_2010 = median_price.x,
         property_price_2020 = median_price.y,
         house_price_2010 = house_price.x,
         house_price_2020 = house_price.y,
         unit_price_2010 = unit_price.x,
         unit_price_2020 = unit_price.y,
         rental_price_2010 = median_rental.x,
         rental_price_2020 = median_rental.y,
         property_count_2010 = property_count.x,
         property_count_2020 = property_count.y,
         house_count_2010 = house_count.x,
         house_count_2020 = house_count.y,
         unit_count_2010 = unit_count.x,
         unit_count_2020 = unit_count.y,
         rental_count_2010 = rental_count.x,
         rental_count_2020 = rental_count.y,
         property_price_change = median_price.y - median_price.x,
         property_price_perc = (median_price.y - median_price.x)/median_price.x,
         house_price_change = house_price.y - house_price.x,
         house_price_perc = (house_price.y - house_price.x)/house_price.x,
         unit_price_change = unit_price.y - unit_price.x,
         unit_price_perc = (unit_price.y - unit_price.x)/unit_price.x,
         rental_price_change = median_rental.y - median_rental.x,
         rental_price_perc = (median_rental.y - median_rental.x)/median_rental.x) %>% 
  dplyr::select(GCC_CODE16,
                property_price_2010,
                property_price_2020,
                house_price_2010,
                house_price_2020,
                unit_price_2010,
                unit_price_2020,
                rental_price_2010,
                rental_price_2020,
                property_count_2010,
                property_count_2020,
                house_count_2010,
                house_count_2020,
                unit_count_2010,
                unit_count_2020,
                rental_count_2010,
                rental_count_2020,
                property_price_change,
                property_price_perc,
                house_price_change,
                house_price_perc,
                unit_price_change,
                unit_price_perc,
                rental_price_change,
                rental_price_perc)


## Export datasets
write.csv(gcc_property_1020, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Outputs/Property Validation/gcc_property_1020.csv")
```

# 3.3 Repeat with SA2 areas
```{r}
# Summarise price for each year
property_2010_median_SA2 <- ddply(property_2010, .(SA2_NAME16, GCC_CODE16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         property_count = length(EventPriceInf) )
property_2020_median_SA2 <- ddply(property_2020, .(SA2_NAME16), dplyr::summarize, 
                         median_price_inf = median(EventPriceInf),
                         median_price = median(EventPrice),
                         property_count = length(EventPriceInf))


house_2010_median_SA2 <- ddply(house_2010, .(SA2_NAME16), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         house_count = length(EventPriceInf) )
house_2020_median_SA2 <- ddply(house_2020, .(SA2_NAME16), dplyr::summarize, 
                         house_price_inf = median(EventPriceInf),
                         house_price = median(EventPrice),
                         house_count = length(EventPriceInf))


unit_2010_median_SA2 <- ddply(unit_2010, .(SA2_NAME16), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         unit_count = length(EventPriceInf) )
unit_2020_median_SA2 <- ddply(unit_2020, .(SA2_NAME16), dplyr::summarize, 
                         unit_price_inf = median(EventPriceInf),
                         unit_price = median(EventPrice),
                         unit_count = length(EventPriceInf))


rental_2010_median_SA2 <- ddply(rental_2010, .(SA2_NAME16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         rental_count = length(EventPriceInf) )
rental_2020_median_SA2 <- ddply(rental_2020, .(SA2_NAME16), dplyr::summarize, 
                         median_rental_inf = median(EventPriceInf),
                         median_rental = median(EventPrice),
                         rental_count = length(EventPriceInf))



# Merge into one dataset
overall_property_1020 <- property_2010_median_SA2 %>% 
  merge(property_2020_median_SA2, by="SA2_NAME16") %>% 
  merge(house_2010_median_SA2, by="SA2_NAME16") %>% 
  merge(house_2020_median_SA2, by="SA2_NAME16") %>% 
  merge(unit_2010_median_SA2, by="SA2_NAME16") %>% 
  merge(unit_2020_median_SA2, by="SA2_NAME16") %>% 
  merge(rental_2010_median_SA2, by="SA2_NAME16") %>% 
  merge(rental_2020_median_SA2, by="SA2_NAME16") %>% 
  mutate(property_price_2010 = median_price.x,
         property_price_2020 = median_price.y,
         house_price_2010 = house_price.x,
         house_price_2020 = house_price.y,
         unit_price_2010 = unit_price.x,
         unit_price_2020 = unit_price.y,
         rental_price_2010 = median_rental.x,
         rental_price_2020 = median_rental.y,
         property_count_2010 = property_count.x,
         property_count_2020 = property_count.y,
         house_count_2010 = house_count.x,
         house_count_2020 = house_count.y,
         unit_count_2010 = unit_count.x,
         unit_count_2020 = unit_count.y,
         rental_count_2010 = rental_count.x,
         rental_count_2020 = rental_count.y,
         property_price_change = median_price.y - median_price.x,
         property_price_perc = (median_price.y - median_price.x)/median_price.x,
         house_price_change = house_price.y - house_price.x,
         house_price_perc = (house_price.y - house_price.x)/house_price.x,
         unit_price_change = unit_price.y - unit_price.x,
         unit_price_perc = (unit_price.y - unit_price.x)/unit_price.x,
         rental_price_change = median_rental.y - median_rental.x,
         rental_price_perc = (median_rental.y - median_rental.x)/median_rental.x) %>% 
  dplyr::select(SA2_NAME16,
                GCC_CODE16,
                property_price_2010,
                property_price_2020,
                house_price_2010,
                house_price_2020,
                unit_price_2010,
                unit_price_2020,
                rental_price_2010,
                rental_price_2020,
                property_count_2010,
                property_count_2020,
                house_count_2010,
                house_count_2020,
                unit_count_2010,
                unit_count_2020,
                rental_count_2010,
                rental_count_2020,
                property_price_change,
                property_price_perc,
                house_price_change,
                house_price_perc,
                unit_price_change,
                unit_price_perc,
                rental_price_change,
                rental_price_perc)


# Gentrification [predicted] hotspots
hotspots <- c('Auburn - Central',
              'Auburn - South',
              'Auburn - North',
              'Bankstown - South',
              'Bankstown - North',
              'Baulkham Hills (East)',
              'Baulkham Hills (West) - Bella Vista',
              'Botany',
              'Eastwood - Denistone',
              'Maroubra - North',
              'Maroubra - South',
              'Maroubra - West',
              'Sutherland - Kirrawee')

hotspot_property_1020 <- overall_property_1020 %>% 
  filter(SA2_NAME16 %in% hotspots)


## Export datasets
write.csv(hotspot_property_1020, "C:/Files/Value Australia/Gentrification ML Prediction/Data/Outputs/Property Validation/hotspot_property_1020_sa2.csv")
```



########## 4. Visualise ##########################

# 4.1 Visualise house prices
```{r}
# Merge on spatial data to pow_11_16
sa1_sf <- cbind(sa1, st_coordinates(st_centroid(sa1)))
house_11_med_sf <- merge(house_11_comb, sa1_sf, by="SA1_MAIN16") %>% st_as_sf() %>% drop_na()
house_16_med_sf <- merge(house_16_comb, sa1_sf, by="SA1_MAIN16") %>% st_as_sf() %>% drop_na()

# Create breaks
house_11_med_sf <- house_11_med_sf %>%
  mutate(median_price_bins = cut2(house_11_med_sf$median_price_inf, c(0, 500000, 750000, 1000000, 1500000, 2000000, 3000000, 4000000) ),
         count_bins = cut2(house_11_med_sf$count, c(0, 10, 50, 100, 200, 500, 1000) ) )

house_16_med_sf <- house_16_med_sf %>%
  mutate(median_price_bins = cut2(house_16_med_sf$median_price_inf, c(0, 500000, 750000, 1000000, 1500000, 2000000, 3000000, 4000000) ),
         count_bins = cut2(house_16_med_sf$count, c(0, 10, 50, 100, 200, 500, 1000) ))


# Visualise
median_11 <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=house_11_med_sf, aes(x=X, y=Y, fill=median_price_bins), colour="transparent") +
  scale_fill_viridis_d("Property Price &\nMedian ($) - 2011") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

count_11 <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=house_11_med_sf, aes(x=X, y=Y, fill=count_bins), colour="transparent") +
  scale_fill_viridis_d("Properties Sold &\n(Count) - 2011", option = "plasma") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 


median_16 <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=house_16_med_sf, aes(x=X, y=Y, fill=median_price_bins), colour="transparent") +
  scale_fill_viridis_d("Property Price &\nMedian ($) - 2016") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

count_16 <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=house_16_med_sf, aes(x=X, y=Y, fill=count_bins), colour="transparent") +
  scale_fill_viridis_d("Properties Sold &\n(Count) - 2016", option = "plasma") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

median_11
median_11 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
count_11 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
median_16
median_16 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
count_16 + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
```


# 4.2 Visualise unit prices
```{r}
# Merge on spatial data to pow_11_16
unit_11_med_sf <- merge(unit_11_comb, sa1_sf, by="SA1_MAIN16") %>% st_as_sf() %>% drop_na()
unit_16_med_sf <- merge(unit_16_comb, sa1_sf, by="SA1_MAIN16") %>% st_as_sf() %>% drop_na()

# Create breaks
unit_11_med_sf <- unit_11_med_sf %>%
  mutate(median_price_bins = cut2(unit_11_med_sf$median_price_inf, c(0, 400000, 600000, 800000, 1000000, 1250000, 1500000, 2000000) ),
         count_bins = cut2(unit_11_med_sf$count, c(0, 10, 50, 100, 200, 500, 1000) ) )

unit_16_med_sf <- unit_16_med_sf %>%
  mutate(median_price_bins = cut2(unit_16_med_sf$median_price_inf, c(0, 400000, 600000, 800000, 1000000, 1250000, 1500000, 2000000) ),
         count_bins = cut2(unit_16_med_sf$count, c(0, 10, 50, 100, 200, 500, 1000) ))


# Visualise
median_11_u <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=unit_11_med_sf, aes(x=X, y=Y, fill=median_price_bins), colour="transparent") +
  scale_fill_viridis_d("Units Price &\nMedian ($) - 2011") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

count_11_u <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=unit_11_med_sf, aes(x=X, y=Y, fill=count_bins), colour="transparent") +
  scale_fill_viridis_d("Units Sold &\n(Count) - 2011", option = "plasma") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 


median_16_u <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=unit_16_med_sf, aes(x=X, y=Y, fill=median_price_bins), colour="transparent") +
  scale_fill_viridis_d("Units Price &\nMedian ($) - 2016") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

count_16_u <- ggplot()+
#  geom_sf(data=sa3_syd, aes(x = X, y = Y), colour="transparent", fill="#440154FF") +
  geom_sf(data=unit_16_med_sf, aes(x=X, y=Y, fill=count_bins), colour="transparent") +
  scale_fill_viridis_d("Units Sold &\n(Count) - 2016", option = "plasma") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) 

median_11_u
median_11_u + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
count_11_u + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
median_16_u
median_16_u + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
count_16_u + coord_sf(xlim = c(150.9, 151.34), ylim = c(-34.05, -33.7))
```

